Hysteresis in human computation:\\ how one task affects another

### 2015-02-10 docs/publications/2014.09_SCIENCE/man.tex
more work on manuscript

Microtask platforms are increasingly popular for the annotation of large
datasets, and obtaining other judgments that require prior knowledge and 
hence are difficult to automate using only a computer.  Due to their 
popularity, there is interest in understanding how various task design factors
influence the reliabality of data obtained using microtask platforms.  
Since tasks are typically bundled together, microtask 
workers tend to perform several similar tasks in quick succession, creating an opportunity for priming effects to induce bias in the results obtained.
Here we describe in detail experiments presented in the main text, in which
we investigate the effect that prior tasks have on the responses given during
subsequent tasks.

@@

The work presented in the main text consisted of six experiments involving
HITs (bundles of microtasks) performed on Amazon's Mechanical Turk platform.  
Each experiment was divided into two treatments.  Treatments for a given 
experiment differed with respect to a particular priming modality, which 
served as the independent variable
(as specified in Table~S\ref{table:experiments}).  
The HITs for treatments of the same experiment always involved the same
test tasks (the last five tasks in the HIT),
the results of which served as the dependent variable.

@@

	Before performing any analysis on the labels that workers provided, we
	performed a series of preprocessing steps.  
	Labels that contained
	multiple words (separated by spaces or punctuation) were split, with
	punctuation removed, and the separated words were treated as distinct 
	features in subsequent analysis.
	Misspelled words were automatically corrected using a spelling 
	correction algorithm described below.  
	Next, words were lemmatized using the
	wordnet lemmatizer \cite{miller1995wordnet,felbaum1998wordnet}.  
	Common words such as ``the'', ``to'', or ``with'', were found using
	NLTK's English stop word list and removed \cite{loper2002nltk}.

>>>>

Microtask platforms are an increasingly popular way to solicit experimental
participants, as well as to annotate large datasets and obtaining other 
judgments that require prior knowledge and 
hence are difficult to automate using only a computer.  Due to their 
popularity, there is interest in understanding how various task design factors
influence the reliabality of data obtained using microtask platforms.  
Since tasks are typically bundled together, microtask 
workers tend to perform several similar tasks in quick succession, creating an opportunity for priming effects to induce bias in the results obtained.
Here we describe in detail experiments presented in the main text, in which
we investigate the effect that prior tasks have on the responses given during
subsequent tasks.

@@

The work presented in the main text consisted of six experiments involving
HITs (bundles of microtasks) performed on Amazon's Mechanical Turk platform.  
The flow of events experienced by a worker when participating in this study 
is depicted in Fig.~S\ref{fig:task_schematic}.  
The steps depicted in an orange box are those
in which the worker interacts with Amazon's Mechanical Turk interface, and 
are the same for any microtask completed on that platform, and similar
on other microtask platforms.  While the steps depicted in a black box 
are specific to our study, the general setup, in which a bundle of tasks
follows instructions, is typical.
\begin{figure}
	\begin{center}
	\includegraphics[scale=0.8]{figs/task_schematic.pdf}
	\caption{Flow of events as experienced by a worker participating in
		our study.  Steps with a dash outlined are only performed by 
		workers assigned to certain treatments 
		(see Table~S\ref{table:experiments}).  Steps outlined in orange are
		part of Amazon's Mechanical Turk interface, and are common to any 
		microtask performed on that platform.  Steps outlined in black are
		specific to our HIT.
	}
	\label{fig:task_schematic}
	\end{center}
\end{figure}

Each experiment was divided into two treatments.  Treatments for a given 
experiment differed with respect to a particular priming modality, which 
served as the independent variable
(as specified in Table~S\ref{table:experiments}).  
The HITs for treatments of the same experiment always involved the same
test tasks (the last five tasks in the HIT),
the results of which served as the dependent variable.

@@

	Before performing any analysis on the labels that workers provided, we
	performed a series of preprocessing steps.  
	Labels that contained
	multiple words (separated by spaces or punctuation) were split, with
	punctuation removed, and the separated words were treated as distinct 
	features in subsequent analysis.
	Misspelled words were automatically corrected using a spelling 
	correction algorithm described below.  
	Next, words were lemmatized using the
	wordnet lemmatizer \cite{miller1995wordnet,felbaum1998wordnet}.  
	Common words such as ``the'', ``to'', or ``with'', were found using
	NLTK's English stop word list \cite{loper2002nltk} and removed.
